Comparative effectiveness of BNT162b2 versus Moderna booster doses in England: preliminary report

### 2022-05-18 write-up/report.Rmd

  outcomes <- 
    c(
      "postest",
      #"covidemergency",
      "covidadmitted",
      "covidadmittedproxy1",
      #"covidcc",
      "coviddeath",
      "noncoviddeath"
    ) %>% 
    set_names(., .)

>>>>

  outcomes <- 
    c(
      "postest",
      #"covidemergency",
      "covidadmitted",
      "covidadmittedproxy1",
      "covidcritcare",
      "coviddeath",
      "noncoviddeath"
    ) %>% 
    set_names(., .)
